abc

### 2024-09-08 randpython.qmd
df2

def genpolycoeff(plr=1,parm=["alpha", "x", "y"],solvd='alpha',eur=[0, 0, 0]):

@@

@@

    sympy.var('alpha x y g h n m zeta Gamma lamda ui')
    expr = [Eq(z,k0+k1*x+k2*y),Eq(z,k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2),Eq(z,k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3)][plr-1]
    sum_eur = sum(eur)
    # Without rotation
    if sum_eur == 0:
        exprc = expr.subs([(z,parm[0]),(x,parm[1]),(y,parm[2])])
        polys = poly(exprc, sympify(solvd)).all_coeffs()
        abc = []
        uvw = []
        ABCDE[:len(polys)] = polys
        return ABCDE 
    # With rotation
    else:

@@

@@

        # Start with non-rotated

@@

@@

                nrs = dxyz[solvd]-1

@@

            B[0] +=  dic['d_320']*u0+dic['d_321']*w0
            B[1] +=  dic['d_302']*u0+dic['d_312']*v0
            B[2] +=  dic['d_301']*w0+dic['d_310']*v0
            C[0] +=  dic['d_310']*u0**2+dic['d_311']*u0*w0+dic['d_312']*w0**2+dic['d_110']
            C[1] +=  dic['d_301']*u0**2+dic['d_311']*u0*v0+dic['d_321']*v0**2+dic['d_101']
            C[2] +=  dic['d_302']*w0**2+dic['d_311']*w0*v0+dic['d_320']*w0**2+dic['d_201']*v0+dic['d_210']*w0+dic['d_110']
            D[0] += dic['d_300']*u0**3+dic['d_301']*w0*u0**2+dic['d_302']*w0**2*u0+dic['d_303']*w0**3
            D[1] += dic['d_300']*u0**3+dic['d_310']*u0*v0**2+dic['d_320']*v0**2*u0+dic['d_330']*v0**3
            D[2] += dic['d_303']*v0**3+dic['d_312']*w0*v0**2+dic['d_321']*w0**2*v0+dic['d_330']*v0**3

@@

            C[0] += dic['d_210']*u0+dic['d_211']*w0
            C[1] += dic['d_201']*u0+dic['d_211']*v0
            C[2] += dic['d_201']*v0+dic['d_210']*w0
            D[0] += dic['d_200']*u0**2+dic['d_201']*w0*u0+dic['d_202']*w0**2
            D[1] += dic['d_200']*u0**2+dic['d_210']*v0*u0+dic['d_220']*v0**2
            D[2] += dic['d_202']*v0**2+dic['d_211']*v0*w0+dic['d_220']*w0**2

@@

            C[2] += dic['d_110']
            D[0] += dic['d_100']*u0+dic['d_101']*w0+dic['d_000']
            D[1] += dic['d_100']*u0+dic['d_110']*v0+dic['d_000']
            D[2] += dic['d_101']*v0+dic['d_110']*w0+dic['d_000']
        ABCDE[0] = A[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
        ABCDE[1] = B[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
        ABCDE[2] = C[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
        ABCDE[3] = D[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])

@@

        return ABCDE, matarch, abc

@@

```{pyodide-python}
genpolycoeff(plr=1,parm=["alpha", "x", "y"], solvd='y') 
genpolycoeff(plr=1,parm=["alpha", "x", "y"], solvd='y',eur=[1, 4, 2])[0]
```

>>>>

def genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g'):
    elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
    x, y, z = sympy.symbols('x y z')
    alpha, g, h, n, m, zeta, Gamma, lamda, ui = symbols('alpha g h n m zeta Gamma lamda ui')
    k0, k1, k2, k3, k4, k5, k6, k7, k8, k9, k10 = symbols('k0:11')
    parm = elem[2-1][:5]
    ls, rs = expr.split('=')
    expr = Eq(sympify(ls), sympify(rs))
    plr = int(sympy.total_degree(expr))-1
    polys = poly(expr.rhs - expr.lhs, sympify(solv)).all_coeffs()
    abc = [1,0,0,0,1,0,0,0,1]
    uvw = []
    ABCDE = [0, 0, 0, 0, 0]
    ABCDE[:len(polys)] = polys
    matarch = 0
    return ABCDE, abc, matarch, plr

#genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')

def genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='y',eur=[1, 2, 4]):
    elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]

@@

    alpha, g, h, n, m, zeta, Gamma, lamda, ui = symbols('alpha g h n m zeta Gamma lamda ui')

@@

    parm = elem[form-1][:5]
    pamm = [element + "_m" for element in parm]
    ls, rs = expr.split('=')
    expr = Eq(sympify(ls), sympify(rs))
    plr = int(sympy.total_degree(expr))-1

@@

    nrs = parm.index(solv)

@@

@@

        #varn.free_symbols

@@

@@

        B[0] += dic['d_320']*z + dic['d_321']*y
        B[1] += dic['d_302']*z + dic['d_312']*x
        B[2] += dic['d_301']*y + dic['d_310']*x
        C[0] += dic['d_310']*z**2 + dic['d_311']*y*z + dic['d_312']*y**2
        C[1] += dic['d_301']*z**2 + dic['d_311']*x*z + dic['d_321']*x**2
        C[2] += dic['d_302']*y**2 + dic['d_311']*x*y + dic['d_320']*x**2
        D[0] += dic['d_300']*y**3 + dic['d_301']*y*z**2 + dic['d_302']*y**2*y+dic['d_303']*z**3
        D[1] += dic['d_300']*x**3 + dic['d_310']*x*y**2 + dic['d_320']*y**2*x+dic['d_330']*y**3
        D[2] += dic['d_303']*y**3 + dic['d_312']*z*y**2 + dic['d_321']*z**2*y + dic['d_330']*y**3

@@

        C[0] += dic['d_210']*z + dic['d_211']*y
        C[1] += dic['d_201']*z + dic['d_211']*x
        C[2] += dic['d_201']*y + dic['d_210']*x
        D[0] += dic['d_200']*z**2 + dic['d_201']*y*z + dic['d_202']*y**2
        D[1] += dic['d_200']*z**2 + dic['d_210']*x*z + dic['d_220']*x**2
        D[2] += dic['d_202']*y**2 + dic['d_211']*x*y + dic['d_220']*x**2

@@

        C[2] += dic['d_100']
        D[0] += dic['d_100']*z + dic['d_101']*y+dic['d_000']
        D[1] += dic['d_100']*z + dic['d_110']*x+dic['d_000']
        D[2] += dic['d_101']*y + dic['d_110']*x+dic['d_000']
    ABCDE[0] = A[nrs].subs([(x,pamm[0]),(y,pamm[1]),(z,pamm[2])])
    ABCDE[1] = B[nrs].subs([(x,pamm[0]),(y,pamm[1]),(z,pamm[2])])
    ABCDE[2] = C[nrs].subs([(x,pamm[0]),(y,pamm[1]),(z,pamm[2])])
    ABCDE[3] = D[nrs].subs([(x,pamm[0]),(y,pamm[1]),(z,pamm[2])])

@@

    return ABCDE, abc, matarch, plr

@@

```{pyodide-python}
#genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')
#genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='alpha',eur=[1, 2, 4])
#genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='x',eur=[1, 2, 4])[0]
#genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='y',eur=[1, 2, 4])[0]
#genpolycoeffr(form=2,expr="z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",solv='alpha',eur=[1, 2, 4])
```
